---
title: "Study Progress"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: readable
    logo: Graphics/insight-logo-horizontal-cropped.png
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(highcharter)
library(treemap)
library(knitr)
library(scales)
library(glue)
library(googleVis)

source("R/datamgmt_progress.R")
source("R/plot_asmts_comp.R")

mosaic_pal <- c(
  ## Row 1, starting with leftmost diamond
  "blue1" = "#283C72", "blue2" = "#243E8B", "blue3" = "#0477BF",
  "green1" = "#8EC63E", "green2" = "#3BB547",
  ## Row 2
  "blue4" = "#24ADCD", "blue5" = "#0976B7", "blue6" = "#23AEDD",
  "green3" = "#3BB54A", "green4" = "#1A653E",
  ## Row 3
  "orange1" = "#E76A32", "orange2" = "#F69723", "orange3" = "#FA961F",
  "orange4" = "#FBCD93", "ecru" = "#FFF8DE",
  ## Row 4
  "red1" = "#D71A60", "red2" = "#F27074", "red3" = "#EC835F",
  "gray1" = "#E4DAD1", "gray2" = "#F7F5EB",
  ## Row 5
  "red4" = "#C0232C", "red5" = "#EE1C27", "red6" = "#FF686D",
  "red7" = "#F8D4D1", "cream" = "#FEFEFC"
)

insight_pal <- c(
  "darkred"    = "#571705",
  "lightred"   = "#d93c02",
  "darkgreen"  = "#455705",
  "lightgreen" = "#7e9f09",
  "darkpurple" = "#170577",
  "darkblue"   = "#054557",
  "darkgold"   = "#866407",
  "lightgold"  = "#cf9a0b"
)

## Function to get hex for a specific element
mosaic_col <- function(hex){ as.character(mosaic_pal[hex]) }
insight_col <- function(hex){ as.character(insight_pal[hex]) }

## Colors for assessment plots
asmt_values = c(
  "Excellent" = insight_col("lightgreen"),
  "Okay"      = insight_col("lightgold"),
  "Uh-oh"     = insight_col("lightred")
)

## Named vector of colors for exclusions
## Treemap palette: c("#571705" (dark red), "#455705" (green), "#054557" (blue))
## Individual exclusions will be variations on that palette
exc_colors <- c(
  ## Informed consent
  ">72h eligibility prior to screening" = "#6f1d06",
  "No surrogate within 72h" = "#571705",
  "Patient/surrogate refusal" = "#872408",
  "Research leadership refusal" = "#9f2a09",
  ## Other exclusions
  "Death within 24h/hospice" = "#455705",
  "Lives >200 miles from VUMC" = "#586f06",
  "Other" = "#6b8708",
  ## Patient characteristics
  "Blind, deaf, English" = "#021f27",
  "Homeless" = "#04323f",
  "Prisoner" = "#054557",
  "Severe cognitive/neuro disorder" = "#06586f",
  "Substance abuse, psych disorder" = "#086b87"
)

## Manually set width, height for screening/enrollment over time plots
screenplot_wd <- 640
screenplot_ht <- 325

```

Screening & Enrollment
=====================================

Column {data-width=60%}
-----------------------------------------------------------------------

### Patients Screened, Approached, and Enrolled

```{r nodate_ids}
nodate_ids <- unique(c(exc_id_nodate)) #, enroll_id_nodate))

nodate_statement <- ifelse(
  length(nodate_ids > 0),
  paste(
    "These IDs have no exclusion/enrollment date entered and are not included:",
    paste(nodate_ids, collapse = "; ")
  ),
  ""
)

```

`r nodate_statement`

```{r screening}
## Want figure to start in November 2017
screening_myears <- unique(screening_summary$myear)
screening_myears_num <- 1:length(screening_myears)
names(screening_myears_num) <- screening_myears

## X axis labels: character versions of unique months of enrollment
## Applies to both screening and exclusion charts
screening_xlabs <- exc_over_time %>%
    dplyr::select(myear, myear_char) %>%
  distinct() %>%
  pull(myear_char)

## Which months to use on X axes? (After a year of enrollment, axis labels
## getting crowded)
use_xlabs <- seq(1, length(screening_xlabs), 2)

screening_summary <- screening_summary %>%
  mutate(myear_num = screening_myears_num[myear])

x_screen <- list(
  tickvals = as.numeric(screening_myears_num)[use_xlabs],
  ticktext = screening_xlabs[use_xlabs],
  title = ""
)
y <- list(title = "")

screen_plotly <- plot_ly(
  data = screening_summary,
  x = ~ myear_num,
  y = ~ Screened,
  type = "bar",
  name = "Screened",
  color = I("#571705"),
  alpha = 0.85,
  hoverinfo = "text",
  text = ~ sprintf("%s, Screened: %s", myear_char, Screened)
) %>%
  add_bars(
    y = ~ Approached,
    name = "Approached",
    color = I("#886407"),
    hoverinfo = "text",
    text = ~ sprintf("%s, Approached: %s", myear_char, Approached)
  ) %>%
  add_bars(
    y = ~ Enrolled,
    name = "Enrolled",
    color = I("#315705"),
    hoverinfo = "text",
    text = ~ sprintf("%s, Enrolled: %s", myear_char, Enrolled)
  )

screen_plotly %>%
  layout(legend = list(x = 0, y = 0.95, bgcolor='transparent'),
         xaxis = x_screen, yaxis = y)

```

### Study Exclusions (% of All Patients Excluded)

```{r exclusions_over_time}
## plotly needs x value to be numeric to sort properly?
exc_myears <- sort(unique(exc_over_time$myear))
exc_myears_num <- 1:length(exc_myears)
names(exc_myears_num) <- exc_myears

exc_over_time <- exc_over_time %>%
  mutate(myear_num = exc_myears_num[myear])

x_exc <- list(tickvals = as.numeric(exc_myears_num)[use_xlabs],
              ticktext = screening_xlabs[use_xlabs],
              title = "")
y_exc <- list(tickvals = seq(0, 100, 20),
              ticktext = paste0(seq(0, 100, 20), "%"),
              title = "Percent of Exclusions")

exc_plotly <- plot_ly(
  data = exc_over_time,
  x = ~ myear_num,
  y = ~ Percent,
  type = "scatter",
  mode = "lines+markers",
  color = ~ Reason,
  colors = exc_colors,
  alpha = 0.6,
  hoverinfo = "text",
  text = ~ sprintf("%s, %s: %s%%", myear_char, Reason, Percent)
)

exc_plotly %>%
  layout(showlegend = FALSE,
         xaxis = x_exc,
         yaxis = y_exc)

```

Column {data-width=40%}
-----------------------------------------------------------------------

### Cumulative Enrollment as of `r format(Sys.Date(), "%B %d, %Y")` {data-height=40%}

```{r enrollment}
screening_statement <- sprintf(
  "We have screened %s patients; %s%% were excluded and %s%% approached. Of those approached, %s%% refused consent and %s%% were enrolled.",
  format(n_screened, big.mark = ","),
  round(pct_excluded*100),
  round(pct_approached*100),
  round(pct_refused*100),
  round(pct_enrolled*100)
)

casemix_statement <- glue(
  "Of the {n_enrolled} enrolled, ",
  "{pct_blunt} ({n_blunt}) experienced blunt trauma; ",
  "{pct_pene} ({n_pene}) experienced penetrating trauma; ",
  "{pct_burn} ({n_burn}) experienced burns; and ",
  "{pct_tbi} ({n_tbi}) experienced TBI."
)

enroll_gauge <- gauge(
  value = n_enrolled,
  min = 0,
  max = n_goal,
  sectors = gaugeSectors(colors = "#866407"),
  label = "patients"
)

enroll_gauge

```
<br>
`r screening_statement`
<br><br>
`r casemix_statement`

### Cumulative Exclusions (Total: `r format(nrow(exc_df), big.mark = ",")`) {data-height=60%}

```{r exclusions_cumulative}
tm_exc <- treemap(dtf = exc_cumul,
                  index = c("reason_type", "Reason"),
                  vSize = "n_reason",
                  type = "index",
                  title = "",
                  algorithm = "squarified",
                  palette = c("#571705", "#455705", "#054557"),
                  draw = FALSE)

hc_tm_exc <- hctreemap(
  tm_exc,
  allowDrillToNode = TRUE,
  layoutAlgorithm = "squarified",
  levels = list(levelIsConstant = "false"),
  dataLabels = list(style = list(color = "white",
                                 textOutline = "0px contrast",
                                 fontSize = "12px"))
)

hc_tm_exc

```

In-Hospital Phase{data-orientation=rows}
================================================================================

Row
--------------------------------------------------------------------------------
```{r ph_prep}
## -- Proportion of full batteries completed -----------------------------------
pct_surrogate_comp <-
  round(mean(all_enrolled$ph_surrogate_comp, na.rm = TRUE) * 100)
pct_caregiver_comp <-
  round(mean(all_enrolled$ph_caregiver_comp, na.rm = TRUE) * 100)

```

### Surrogate %{data-width=35%}

```{r ph_surrogate}
valueBox(
  value = paste0(pct_surrogate_comp, "%"),
  caption =
    "completed pre-hospital surrogate questionnaires<br><i>(General, B/IADLs, NIDA, LS, employment, income, Grit, BDI, attitude toward donation)</i>",
  color = ifelse(
    pct_surrogate_comp < 80, insight_col("lightred"), insight_col("lightgreen")
  ),
  icon = "ion-people"
)

```

### Caregiver %{data-width=35%}

```{r ph_caregiver}
valueBox(
  value = paste0(pct_caregiver_comp, "%"),
  caption =
    "completed caregiver questionnaires<br><i>(Zarit, Memory & Behavior)</i>",
  color = ifelse(
    pct_caregiver_comp < 80, insight_col("lightred"), insight_col("lightgreen")
  ),
  icon = "ion-heart"
)

```

### Surrogate/Caregiver Battery Completion{width=150%}
```{r surrogate_pctcomp_ind}
p_surr <- plot_asmts_comp(df = surrogate_pctcomp, ybreaks = seq(0, 1, 0.2))
ggplotly(p_surr, tooltip = "text")

```

Row
--------------------------------------------------------------------------------
### Specimen Log Compliance (% of Patients Eligible)
```{r specimen_compliance}
## Color palette
specimen_colors <- c(
  "blue" = insight_col("darkblue"),
  "green" = insight_col("darkgreen"),
  "purple" = insight_col("darkpurple"),
  "red" = insight_col("darkred")
)

## Add text for tooltips
specimen_df$htext <- glue::glue_data(
  specimen_df,
  "{Day}, {Color}: {scales::percent(Compliance)}"
)
specimen_plot <- ggplot(
  data = specimen_df, aes(x = Day, y = Compliance, text = htext)
) +
  geom_pointrange(
    aes(ymin = 0, ymax = Compliance, color = Color),
    size = 3, position = position_dodge(width = 0.7)
  ) +
  scale_y_continuous(limits = c(0, 1),
                     breaks = seq(0, 1, 0.5),
                     label = scales::percent) +
  scale_color_manual(values = specimen_colors, guide = FALSE) +
  scale_alpha_manual(values = c(0.65, 0.85)) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text = element_text(size = 10),
        panel.background = element_rect(fill = NA, color = "gray80"),
        panel.spacing = unit(2, "lines"))
x <- y <- list(title = NULL)
specimen_plot %>%
  ggplotly(tooltip = "text") %>%
  layout(xaxis = x, yaxis = y)

```

### Current In-Hospital Status
```{r current_status}
## List of patients currently in hospital
pts_inhosp <- subset(all_enrolled, inhosp_status == "Still in hospital")$id
pts_inhosp_text <- ifelse(length(pts_inhosp) == 0, "None",
                          paste0(pts_inhosp, collapse = "; "))
tm_status <- treemap(
  dtf = status_count,
  index = c("inhosp_status"),
  vSize = "n_status",
  type = "index",
  title = "",
  algorithm = "squarified",
  palette = insight_pal[c("darkblue", "darkred", "darkgreen", "darkpurple")],
  draw = FALSE
)
hc_tm_status <- hctreemap(
  tm_status,
  allowDrillToNode = TRUE,
  layoutAlgorithm = "squarified",
  levels = list(levelIsConstant = "false"),
  dataLabels = list(style = list(color = "white",
                                 textOutline = "0px contrast",
                                 fontSize = "12px"))
) %>%
  hc_subtitle(
    text = paste("Patients currently in hospital:", pts_inhosp_text),
    align = "left"
  )
hc_tm_status
```

Follow-Up {data-orientation=rows}
================================================================================
Row
--------------------------------------------------------------------------------

```{r fu_prep}
prop_totals_pt <- map_dbl(
  fu_totals %>% pull(prop_comp_pt), ~ round(., 2)
) %>%
  set_names(fu_totals %>% pull(redcap_event_name))
prop_totals_cg <- map_dbl(
  fu_totals %>% pull(prop_comp_cg), ~ round(., 2)
) %>%
  set_names(fu_totals %>% pull(redcap_event_name))

fu_asmts <- fu_asmts %>%
  mutate(
    asmt_type = case_when(
      asmt_type == "brain_comp"        ~ "Donation",
      asmt_type == "cd_comp"           ~ "CD-RISC",
      asmt_type == "cg_comp"           ~ "CG Gen.",
      asmt_type == "cog_comp"          ~ "Cognitive",
      asmt_type == "driving_care_comp" ~ "Driving (CG)",
      asmt_type == "driving_comp"      ~ "Driving (PT)",
      asmt_type == "emp_comp"          ~ "Emp.",
      asmt_type == "gq_comp"           ~ "Gen.",
      asmt_type == "hand_comp"         ~ "Hand.",
      asmt_type == "mb_comp"           ~ "M/B",
      asmt_type == "social_comp"       ~ "Social",
      asmt_type == "zarit_comp"        ~ "Zarit",
      TRUE ~ toupper(str_remove(asmt_type, "\\_comp$"))
    ),
    htext = paste0(asmt_type, ": ", scales::percent(round(prop_comp, 2))),
    comp_ok = case_when(
      prop_comp > 0.90 ~ "Excellent",
      prop_comp > 0.80 ~ "Okay",
      TRUE             ~ "Uh-oh"
    )
  )

```

### 3-Month Follow-Up, Patients{data-width=25%}
```{r fu_pt_3m}
valueBox(
  value = scales::percent(pluck(prop_totals_pt, "3 Month Assessment")),
  caption = "<b>patient assessments</b> fully or partially completed,<br><b>3 months</b>",
  color = case_when(
    pluck(prop_totals_pt, "3 Month Assessment") < 0.8 ~ asmt_values[["Uh-oh"]],
    pluck(prop_totals_pt, "3 Month Assessment") < 0.9 ~ asmt_values[["Okay"]],
    TRUE ~ asmt_values[["Excellent"]]
  )
)

```

### 3-Month Follow-Up, Caregivers{data-width=25%}
```{r fu_cg_3m}
valueBox(
  value = scales::percent(pluck(prop_totals_cg, "3 Month Assessment")),
  caption = "<b>caregiver assessments</b> fully or partially completed,<br><b>3 months</b>",
  color = case_when(
    pluck(prop_totals_cg, "3 Month Assessment") < 0.8 ~ asmt_values[["Uh-oh"]],
    pluck(prop_totals_cg, "3 Month Assessment") < 0.9 ~ asmt_values[["Okay"]],
    TRUE ~ asmt_values[["Excellent"]]
  )
)

```

### Assessments {data-width=20%}
```{r fu_asmts_3m}
p_3m <- plot_asmts_comp(
  df = fu_asmts %>%
    filter(
      redcap_event_name == "3 Month Assessment",
      asmt_type %in% c("Cognitive", "Emp.")
    ),
  ybreaks = 0:1,
  order_desc = FALSE
)

ggplotly(p_3m + theme(axis.text.y = element_blank()), tooltip = "text")

```

Study & Technical Info
=====================================

INSIGHT-ICU is funded by the National Institutes of Health. Please see our
listing on [clinicaltrials.gov](https://clinicaltrials.gov/ct2/show/NCT03098459).

This dashboard uses `r devtools::session_info()$platform$version`. Packages:

```{r}
DT::datatable(devtools::session_info()$packages)

```