---
title: "Study Progress"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: readable
    logo: Graphics/insight-logo-horizontal-cropped.png
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(highcharter)
library(treemap)
library(knitr)
library(scales)
library(glue)
library(googleVis)

source("R/datamgmt_progress.R")
source("R/plot_asmts_comp.R")

mosaic_pal <- c(
  ## Row 1, starting with leftmost diamond
  "blue1" = "#283C72", "blue2" = "#243E8B", "blue3" = "#0477BF",
  "green1" = "#8EC63E", "green2" = "#3BB547",
  ## Row 2
  "blue4" = "#24ADCD", "blue5" = "#0976B7", "blue6" = "#23AEDD",
  "green3" = "#3BB54A", "green4" = "#1A653E",
  ## Row 3
  "orange1" = "#E76A32", "orange2" = "#F69723", "orange3" = "#FA961F",
  "orange4" = "#FBCD93", "ecru" = "#FFF8DE",
  ## Row 4
  "red1" = "#D71A60", "red2" = "#F27074", "red3" = "#EC835F",
  "gray1" = "#E4DAD1", "gray2" = "#F7F5EB",
  ## Row 5
  "red4" = "#C0232C", "red5" = "#EE1C27", "red6" = "#FF686D",
  "red7" = "#F8D4D1", "cream" = "#FEFEFC"
)

## Function to get hex for a specific element
mosaic_col <- function(hex){ as.character(mosaic_pal[hex]) }

## Colors for assessment plots
asmt_values = c(
  "Excellent" = mosaic_col("green4"),
  "Okay" = mosaic_col("orange3"),
  "Uh-oh" = mosaic_col("red5")
)

# ## Named vector of colors for exclusions
# exc_colors <- c(
#   ">5 hospital days in last 30" = mosaic_col("blue1"),
#   "Severe neurologic injury" = mosaic_col("blue3"),
#   "Death within 24h/hospice" = mosaic_col("blue4"),
#   "Rapidly resolving organ failure" = mosaic_col("blue5"),
#   "BMI > 50" = mosaic_col("red1"),
#   "Substance abuse, etc" = mosaic_col("red2"),
#   "Blind, deaf, English" = mosaic_col("red3"),
#   "Prisoner" = mosaic_col("red4"),
#   "Inability to live independently" = mosaic_col("red5"),
#   "Homeless" = mosaic_col("red6"),
#   "Patient/surrogate refusal" = mosaic_col("green4"),
#   "No surrogate within 72h" = mosaic_col("green1"),
#   "Attending refusal" = mosaic_col("green3"),
#   ">72h eligibility prior to screening" = mosaic_col("green4"),
#   "Lives >150 miles from VUMC" = mosaic_col("orange1"),
#   "Study with no co-enrollment" = mosaic_col("orange2"),
#   "Other" = mosaic_col("orange3")
# )

## Manually set width, height for screening/enrollment over time plots
screenplot_wd <- 640
screenplot_ht <- 325

```

Screening & Enrollment
=====================================

Column {data-width=60%}
-----------------------------------------------------------------------

### Patients Screened, Approached, and Enrolled

```{r nodate_ids}
nodate_ids <- unique(c(exc_id_nodate)) #, enroll_id_nodate))

nodate_statement <- ifelse(
  length(nodate_ids > 0),
  paste(
    "These IDs have no exclusion/enrollment date entered and are not included:",
    paste(nodate_ids, collapse = "; ")
  ),
  ""
)

```

`r nodate_statement`

```{r screening}
## Want figure to start in November 2017
screening_myears <- unique(screening_summary$myear)
screening_myears_num <- 1:length(screening_myears)
names(screening_myears_num) <- screening_myears

## X axis labels: character versions of unique months of enrollment
## Applies to both screening and exclusion charts
screening_xlabs <- exc_over_time %>%
    dplyr::select(myear, myear_char) %>%
  distinct() %>%
  pull(myear_char)

## Which months to use on X axes? (After a year of enrollment, axis labels
## getting crowded)
use_xlabs <- seq(1, length(screening_xlabs), 2)

screening_summary <- screening_summary %>%
  mutate(myear_num = screening_myears_num[myear])

x_screen <- list(
  tickvals = as.numeric(screening_myears_num)[use_xlabs],
  ticktext = screening_xlabs[use_xlabs],
  title = ""
)
y <- list(title = "")

screen_plotly <- plot_ly(
  data = screening_summary,
  x = ~ myear_num,
  y = ~ Screened,
  type = "bar",
  name = "Screened",
  color = I("#571705"),
  alpha = 0.85,
  hoverinfo = "text",
  text = ~ sprintf("%s, Screened: %s", myear_char, Screened)
) %>%
  add_bars(
    y = ~ Approached,
    name = "Approached",
    color = I("#886407"),
    hoverinfo = "text",
    text = ~ sprintf("%s, Approached: %s", myear_char, Approached)
  ) %>%
  add_bars(
    y = ~ Enrolled,
    name = "Enrolled",
    color = I("#315705"),
    hoverinfo = "text",
    text = ~ sprintf("%s, Enrolled: %s", myear_char, Enrolled)
  )

screen_plotly %>%
  layout(legend = list(x = 0, y = 0.95, bgcolor='transparent'),
         xaxis = x_screen, yaxis = y)

```

### Study Exclusions (% of All Patients Excluded)

```{r exclusions_over_time}
## plotly needs x value to be numeric to sort properly?
exc_myears <- sort(unique(exc_over_time$myear))
exc_myears_num <- 1:length(exc_myears)
names(exc_myears_num) <- exc_myears

exc_over_time <- exc_over_time %>%
  mutate(myear_num = exc_myears_num[myear])

x_exc <- list(tickvals = as.numeric(exc_myears_num)[use_xlabs],
              ticktext = screening_xlabs[use_xlabs],
              title = "")
y_exc <- list(tickvals = seq(0, 100, 20),
              ticktext = paste0(seq(0, 100, 20), "%"),
              title = "Percent of Exclusions")

exc_plotly <- plot_ly(
  data = exc_over_time,
  x = ~ myear_num,
  y = ~ Percent,
  type = "scatter",
  mode = "lines+markers",
  color = ~ Reason,
  # colors = exc_colors,
  alpha = 0.6,
  hoverinfo = "text",
  text = ~ sprintf("%s, %s: %s%%", myear_char, Reason, Percent)
)

exc_plotly %>%
  layout(showlegend = FALSE,
         xaxis = x_exc,
         yaxis = y_exc)

```

Column {data-width=40%}
-----------------------------------------------------------------------

### Cumulative Enrollment as of `r format(Sys.Date(), "%B %d, %Y")` {data-height=40%}

```{r enrollment}
screening_statement <- sprintf(
  "We have screened %s patients; %s%% were excluded and %s%% approached. Of those approached, %s%% refused consent and %s%% were enrolled.",
  format(n_screened, big.mark = ","),
  round(pct_excluded*100),
  round(pct_approached*100),
  round(pct_refused*100),
  round(pct_enrolled*100)
)

enroll_gauge <- gauge(
  value = n_enrolled,
  min = 0,
  max = n_goal,
  sectors = gaugeSectors(colors = "#866407"),
  label = "patients"
)

enroll_gauge

```
<br>
`r screening_statement`

### Cumulative Exclusions (Total: `r format(nrow(exc_df), big.mark = ",")`) {data-height=60%}

```{r exclusions_cumulative}
tm_exc <- treemap(dtf = exc_cumul,
                  index = c("reason_type", "Reason"),
                  vSize = "n_reason",
                  type = "index",
                  title = "",
                  algorithm = "squarified",
                  palette = c("#571705", "#455705", "#054557"),
                  draw = FALSE)

hc_tm_exc <- hctreemap(
  tm_exc,
  allowDrillToNode = TRUE,
  layoutAlgorithm = "squarified",
  levels = list(levelIsConstant = "false"),
  dataLabels = list(style = list(color = "white",
                                 textOutline = "0px contrast",
                                 fontSize = "12px"))
)

hc_tm_exc

```

Study & Technical Info
=====================================

INSIGHT-ICU is funded by the National Institutes of Health. Please see our
listing on [clinicaltrials.gov](https://clinicaltrials.gov/ct2/show/NCT03098459).

This dashboard uses `r devtools::session_info()$platform$version`. Packages:

```{r}
DT::datatable(devtools::session_info()$packages)

```